A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-29 4_method.tex
rewrite section on properties of significance measure

\subsection{Beading}
We assign a bead count to each node in the skeleton which is connected to a bone which is in `the center' of the shape
and also to each node with locally optimal feature radius $R$.
Around regions where the bead count changes we introduce transition regions.

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill.
Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.

@@

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of significant regions.

@@

The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: \cref{distance_ratio_limit}.

Any node in the skeleton can have at most two significant bones connected to it, because we have limited $\alpha_\text{max} > 120\degree$,
while the corners of a triangle can only add up to \SI{180}{\degree}.
\todo{TODO: make figure which clearly shows this!}
This results in the fact that we will never have 3-way intersections of non-closed extrusion toolpaths.
(Simple case) If 2 edges of the ST meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
However, what if we connect two significant segments using a small insignificant segment?
There is a distance limit based on \cref{distance_ratio_limit}:
the connecting segment is always larger in Euclidean distance than the difference in feature radius $R$.

\subsubsection{Properties of significant regions}
A node in the graph can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.

A saddle point is always marked.
When going from one local maximum to another we must pass through a significant region.
You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
This menas that the feature radius function in between marked regions is monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.

From any node in the graph which is not a saddle point there is at most a single edge going upward.
Any branch point $v$ in the VD coincides with the circumcircle of its support $p_1, p_2, p_3$.
If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_1 p_2 p_3$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_1 + \angle p_2 = \angle p_3$.
Then a circle with radius $R(v) + \epsilon$ around $w$ such that $|v-w| < 2 \epsilon$ can only touch $p_1$ and $p_3$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
This means that walking up the graph from a marked region to a local maximum follows a single path without branching.

@@

The two downward edges from a branch point cannot both be significant.
A branch point which is not a local maximum generated by the support points $p_1, p_2, p_3$ has bisector angles such that $\triangle p_1 p_2 p_3$ has its circumcentre $v$ outside of the triangle, because otherwise the feature radius decreases in all directions.
This means that all support points lie within a \SI{180}{\degree} range around the node. 
Suppose the one edge going upward is generated by $p_1$ and $p_3$.
Then the bisector angle $\angle p_1 v p_3 < 180\degree$ and $\angle p_1 v p_2 + \angle p_2 v p_3 < 180\degree$,
so if $\angle p_1 v p_2 < 120\degree$ then $\angle p_2 v p_3 < 60\degree$ and is therefore not significant. 
%so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.

>>>>

\subsection{Beading}
We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which intuitively look like `the center' of the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the skeleton.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

@@

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
See \cref{distance_based_angles}.
This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of significant regions.

@@

\subsubsection{Properties of significant regions}
The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: see \cref{distance_ratio_limit}.
The distance $|v - p| = \Delta R$ exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
A node in the graph can have at most two significant edges.
For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
% However, because of some filtering operations this property does not neccesarily hold for the markings.
The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
so the nodes of the ST also have at most two significant edges.
\fi

A saddle point is always marked, i.e.\
when traversing the skeletal graph from one locally maximum $R$ to another we must pass through a significant region.
You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
This means that the feature radius function in between marked regions is always monotonic.
This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.

From any node in the graph which is not a saddle point there is at most a single edge going upward.
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_1, p_2, p_3$.
If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_1 p_2 p_3$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_1 + \angle p_2 = \angle p_3$.
Then a circle with radius $R(v) + \epsilon$ around $w$ such that $|v-w| < 2 \epsilon$ can only touch $p_1$ and $p_3$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
This means that walking up the graph from a marked region to a local maximum follows a single path without branching.

@@

\iffalse
% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
The two downward edges from a branch point cannot both be significant.
A branch point which is not a local maximum generated by the support points $p_1, p_2, p_3$ has bisector angles such that $\triangle p_1 p_2 p_3$ has its circumcentre $v$ outside of the triangle, because otherwise the feature radius decreases in all directions.
This means that all support points lie within a \SI{180}{\degree} range around the node. 
Suppose the one edge going upward is generated by $p_1$ and $p_3$.
Then the bisector angle $\angle p_1 v p_3 < 180\degree$ and $\angle p_1 v p_2 + \angle p_2 v p_3 < 180\degree$,
so if $\angle p_1 v p_2 < 120\degree$ then $\angle p_2 v p_3 < 60\degree$ and is therefore not significant. 
%so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.
\fi
